Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2018-05-01 Ben_Manuscripts/structure_paper/Outline.tex
New figures

>>>>

  \begin{figure}
  \centering
  \begin{subfigure}{0.32\textwidth}
        \includegraphics[width=1\linewidth]{sodium_density.png}
        \caption{Sodium Ions}
        \label{fig:sodium_regional_density}
  \end{subfigure}
  \begin{subfigure}{0.32\textwidth}
        \includegraphics[width=1\linewidth]{head_group_density.png}
        \caption{Head Groups}
        \label{fig:head_groups_regional_density}
  \end{subfigure}
  \begin{subfigure}{0.32\textwidth}
        \includegraphics[width=1\linewidth]{tails_density.png}
        \caption{Tails}
        \label{fig:tails_regional_density}
  \end{subfigure}
  \caption{Alternate figure : In all cases, the component radial distribution functions exhibit a
	  composition gradient transitioning from the hydrophilic to the hydrophobic
	  regions. Systems with layers initially spaced 3.7 \AA~apart in the  parallel
	  displaced (a), and sandwiched (b) configurations both show the highest
	  concentrations of ions and head groups away from the pore center. Systems with
	  layers initially spaced 5 \AA~apart (c) and (d), both show the highest
	  concentrations of ions and head groups near the pore center, implying a more
	  uniform, disordered pore.}~\label{fig:overlaid_densities}
  \end{figure}
